---
title: "DEA Assessgnment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
###Requirements
1-Perform DEA analysis by under all DEA assumptions of FDH, CRS, VRS, IRS, DRS, and FRH.
2-Determine the Peers and Lambdas under each of the above assumptions. 
3-Summarize your results in a tabular format.
4-If possible, plot the frontier function for each part (similar to Page 20 in our notes)

###CRS
The original constant return to scale crs model.
1. We nned to figure out the peers and lamda code, then we could get the peers and labda of each assumptions.
```{r}
library(lpSolveAPI)
library(ucminf)
library(Benchmarking)
s <- matrix(c(150,400,320,520,350,320,0.2,0.7,1.2,2,1.2,0.7),ncol = 2)
q <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000), ncol=2)
p <- dea(s,q,RTS = "crs")
p
peers(p)
lambda(p)
rowSums(s)
rowSums(q)
dea.plot( rowSums(s),rowSums(q),RTS="crs")
z <- as.data.frame(matrix(c(s,q),ncol=4))
z
library(ggplot2)
ggplot(data=z,aes(V2,V3)) +
  geom_line(aes(color="red")) +
  geom_line(aes(V2,V4),color="yellow",show.legend = T)
```
###Remarks
From the crs, we could see that the facility 1-4 are efficient. The facility 5-6 are not inefficient. So that the result is to increase the efficiency.We could also see that the facility 5-6 are updated by closer to the other facilities. 

###VRS
The varing return to scale models.
```{r}
library(lpSolveAPI)
library(ucminf)
library(Benchmarking)
s <- matrix(c(150,400,320,520,350,320,.2,.7,1.2,2,1.2,.7),ncol = 2)
q <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000), ncol=2)
p <- dea(s,q,RTS = "vrs")
p
peers(p)
lambda(p)
rowSums(s)
rowSums(q)
dea.plot( rowSums(s),rowSums(q),RTS="vrs",wx=0.01,wy=0.01)
```
###Remarks
From the vrs, we could see that the facility 6 is inefficient, 

###IRS
The increasing return to scale model.
```{r}
library(lpSolveAPI)
library(ucminf)
library(Benchmarking)
s <- matrix(c(150,400,320,520,350,320,.2,.7,1.2,2,1.2,.7),ncol = 2)
q <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000), ncol=2)
p <- dea(s,q,RTS = "irs")
p
peers(p)
lambda(p)
rowSums(s)
rowSums(q)
dea.plot( rowSums(s),rowSums(q),RTS="irs",wx=0.01,wy=0.01)
```
###Remarks
From the Irs, we could see that only the facility 6 is inefficient. 

###DRS
The decreasing return to scale model.
```{r}
library(lpSolveAPI)
library(ucminf)
library(Benchmarking)
s <- matrix(c(150,400,320,520,350,320,.2,.7,1.2,2,1.2,.7),ncol = 2)
q <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000), ncol=2)
p <- dea(s,q,RTS = "drs")
p
peers(p)
lambda(p)
rowSums(s)
rowSums(q)
dea.plot( rowSums(s),rowSums(q),RTS="drs",wx=0.01,wy=0.01)
```
###Remarks
From the drs, we could see that both facility 5 and 6 are inefficient, The facility 5 could be pdated by closing to the facility 1,2 and 4 and the coefficient should be the lambda values. the facility 6 should be updated by using the facility 1,2 and 4 the coeficient should be the lambda values. 

###FDH
The free disposability hull model.
```{r}
library(lpSolveAPI)
library(ucminf)
library(Benchmarking)
s <- matrix(c(150,400,320,520,350,320,.2,.7,1.2,2,1.2,.7),ncol = 2)
q <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000), ncol=2)
p <- dea(s,q,RTS = "fdh", ORIENTATION = 2)
p
peers(p)
lambda(p)
rowSums(s)
rowSums(q)
dea.plot( rowSums(s),rowSums(q),RTS="fdh",wx=0.01,wy=0.01)
```
###Remarks
From the FDH, we could see that all facilities are efficient. 

###FRH
The free replicability hull models.
Since the FRH use the code add, we just change the frh into add below to get the FRH result.
```{r}
library(lpSolveAPI)
library(ucminf)
library(Benchmarking)
s <- matrix(c(150,400,320,520,350,320,.2,.7,1.2,2,1.2,.7),ncol = 2)
q <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000), ncol=2)
p <- dea(s,q,RTS = "add")
p
peers(p)
lambda(p)
rowSums(s)
rowSums(q)
dea.plot( rowSums(s),rowSums(q),RTS="add",wx=0.01,wy=0.01)
```
###Remarks
From FRH, we could see that all facilities are all efficient. 
Under FRH, all facilities are all efficient.


































